Agile Inter-team Software Development

### 2019-01-20 Draft/Draft.tex
Added image for Spotify. Fix CCS information.

@@

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

\settopmatter{printacmref=false}						%RA: get rid of dumb ACM reference format BLAH BLAH

@@

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

@@

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful taxonomic tools for you to help readers find your work in an online search.

The ACM Computing Classification System --- \url{https://www.acm.org/publications/class-2012} --- is a set of classifiers and concepts that describe the computing discipline. Authors can select entries from this classification system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases of the authors' choosing, providing a more flexible way of describing the research being presented.

CCS concepts and user-defined keywords are required for all short- and full-length articles, and optional for two-page abstracts.

>>>>

\usepackage{graphicx}

@@

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[SER574 '19]{SER574 '19: Advanced Software Design}{January 20, 2019}{Mesa, AZ}
\acmBooktitle{SER574 '19: Advanced Software Design, January 20, 2019, Mesa, AZ}
\acmPrice{1500.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

%RA: remove the BLAH BLAH
%see  https://tex.stackexchange.com/questions/346292/how-to-remove-conference-information-from-the-acm-2017-sigconf-template
%\settopmatter{printacmref=false}						   %ACM reference format BLAH BLAH
\renewcommand\footnotetextcopyrightpermission[1]{} %ACM premission thing
%\pagestyle{plain}														 %ACM running header

@@

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011081.10011082.10011083</concept_id>
<concept_desc>Software and its engineering~Agile software development</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011074.10011134.10011135</concept_id>
<concept_desc>Software and its engineering~Programming teams</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003490.10003491.10003492</concept_id>
<concept_desc>Social and professional topics~Project management techniques</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Agile software development}
\ccsdesc[300]{Software and its engineering~Programming teams}
\ccsdesc[300]{Social and professional topics~Project management techniques}

@@

### 2019-01-20 Draft/Parts/Main.tex
Added image for Spotify. Fix CCS information.

\section{NAME ME} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analgous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

%add image

>>>>

\section{Spotify: A Canonical Example} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
  \caption{Agile team organization at Spotify \cite{kniberg12}.}
  \label{fig:spotify_structure}
\end{figure}
